07_summary_stats

### 2023-09-13 07_summary_stats.Rmd
Update 07_summary_stats.Rmd
removed broadband metrics

```{r setup, include=FALSE}
library(tidyverse)
```

@@

Read in RDA files for percentiles
```{r}
## Make list of rda files to read in
pclist <- c("BB_pct01_07", "BB_pct01_08", "BB_pct01_10", "BB_pct01_12", "BB_pct01_13", "BB_pct01_14", "BB_pct01_16", 
            "BB_pct01_18", "BB_pct01_19", "BB_pct01_20", "BB_pct01_21", "BB_pct01_22", "BB_pct01_23", "TO_pct01_07",
            "TO_pct01_08", "TO_pct01_10", "TO_pct01_12", "TO_pct01_13", "TO_pct01_14", "TO_pct01_16", "TO_pct01_18", 
            "TO_pct01_19", "TO_pct01_20", "TO_pct01_21", "TO_pct01_22", "TO_pct01_23", "BB_pct99_07", "BB_pct99_08", 
            "BB_pct99_10", "BB_pct99_12", "BB_pct99_13", "BB_pct99_14", "BB_pct99_16", "BB_pct99_18", "BB_pct99_19", 
            "BB_pct99_20", "BB_pct99_21", "BB_pct99_22", "BB_pct99_23", "TO_pct99_07", "TO_pct99_08", "TO_pct99_10", 
            "TO_pct99_12", "TO_pct99_13", "TO_pct99_14", "TO_pct99_16", "TO_pct99_18", "TO_pct99_19", "TO_pct99_20", 
            "TO_pct99_21", "TO_pct99_22", "TO_pct99_23")

@@

# 1 Percentile
pct01_07 <- cbind(BB_pct01_07, TO_pct01_07) %>%
  select(., -3)
pct01_08 <- cbind(BB_pct01_08, TO_pct01_08) %>%
  select(., -3)
pct01_10 <- cbind(BB_pct01_10, TO_pct01_10) %>%
  select(., -3)
pct01_12 <- cbind(BB_pct01_12, TO_pct01_12) %>%
  select(., -3)
pct01_13 <- cbind(BB_pct01_13, TO_pct01_13) %>%
  select(., -3)
pct01_14 <- cbind(BB_pct01_14, TO_pct01_14) %>%
  select(., -3)
pct01_16 <- cbind(BB_pct01_16, TO_pct01_16) %>%
  select(., -3)
pct01_18 <- cbind(BB_pct01_18, TO_pct01_18) %>%
  select(., -3)
pct01_19 <- cbind(BB_pct01_19, TO_pct01_19) %>%
  select(., -3)
pct01_20 <- cbind(BB_pct01_20, TO_pct01_20) %>%
  select(., -3)
pct01_21 <- cbind(BB_pct01_21, TO_pct01_21) %>%
  select(., -3)
pct01_22 <- cbind(BB_pct01_22, TO_pct01_22) %>%
  select(., -3)
pct01_23 <- cbind(BB_pct01_23, TO_pct01_23) %>%
  select(., -3)

pct01_all <- rbind(pct01_07, pct01_08, pct01_10, pct01_12, pct01_13,
                   pct01_14, pct01_16, pct01_18, pct01_19, pct01_20,
                   pct01_21, pct01_22, pct01_23)
# need to add column with buoy name

# 99 Percentile
pct99_07 <- cbind(BB_pct99_07, TO_pct99_07) %>%
  select(., -3)
pct99_08 <- cbind(BB_pct99_08, TO_pct99_08) %>%
  select(., -3)
pct99_10 <- cbind(BB_pct99_10, TO_pct99_10) %>%
  select(., -3)
pct99_12 <- cbind(BB_pct99_12, TO_pct99_12) %>%
  select(., -3)
pct99_13 <- cbind(BB_pct99_13, TO_pct99_13) %>%
  select(., -3)
pct99_14 <- cbind(BB_pct99_14, TO_pct99_14) %>%
  select(., -3)
pct99_16 <- cbind(BB_pct99_16, TO_pct99_16) %>%
  select(., -3)
pct99_18 <- cbind(BB_pct99_18, TO_pct99_18) %>%
  select(., -3)
pct99_19 <- cbind(BB_pct99_19, TO_pct99_19) %>%
  select(., -3)
pct99_20 <- cbind(BB_pct99_20, TO_pct99_20) %>%
  select(., -3)
pct99_21 <- cbind(BB_pct99_21, TO_pct99_21) %>%
  select(., -3)
pct99_22 <- cbind(BB_pct99_22, TO_pct99_22) %>%
  select(., -3)
pct99_23 <- cbind(BB_pct99_23, TO_pct99_23) %>%
  select(., -3)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(PAMpal)
library(PAMmisc)
library(PAMscapes)
library(patchwork)
library(knitr)
library(kableExtra)
```

@@

Read in RDA files for percentiles
```{r}
## Make list of rda files to read in
pclist <- c("pct10_07", "pct10_08", "pct10_10", "pct10_12", "pct10_13",
            "pct10_14", "pct10_16", "pct10_18", "pct10_19", "pct10_20",
            "pct10_21", "pct10_22", "pct10_23", "pct90_07", "pct90_08",
            "pct90_10", "pct90_12", "pct90_13", "pct90_14", "pct90_16",
            "pct90_18", "pct90_19", "pct90_20", "pct90_21", "pct90_22",
            "pct90_23", "pct50_07", "pct50_08", "pct50_10", "pct50_12",
            "pct50_13", "pct50_14", "pct50_16", "pct50_18", "pct50_19", 
            "pct50_20", "pct50_21", "pct50_22", "pct50_23")

@@

Create df from 1 percentile
```{r}
# 1 Percentile
pct01_07 <- cbind(BB_pct01_07, TO_pct01_07) %>%
  select(., -3)
pct01_08 <- cbind(BB_pct01_08, TO_pct01_08) %>%
  select(., -3)
pct01_10 <- cbind(BB_pct01_10, TO_pct01_10) %>%
  select(., -3)
pct01_12 <- cbind(BB_pct01_12, TO_pct01_12) %>%
  select(., -3)
pct01_13 <- cbind(BB_pct01_13, TO_pct01_13) %>%
  select(., -3)
pct01_14 <- cbind(BB_pct01_14, TO_pct01_14) %>%
  select(., -3)
pct01_16 <- cbind(BB_pct01_16, TO_pct01_16) %>%
  select(., -3)
pct01_18 <- cbind(BB_pct01_18, TO_pct01_18) %>%
  select(., -3)
pct01_19 <- cbind(BB_pct01_19, TO_pct01_19) %>%
  select(., -3)
pct01_20 <- cbind(BB_pct01_20, TO_pct01_20) %>%
  select(., -3)
pct01_21 <- cbind(BB_pct01_21, TO_pct01_21) %>%
  select(., -3)
pct01_22 <- cbind(BB_pct01_22, TO_pct01_22) %>%
  select(., -3)
pct01_23 <- cbind(BB_pct01_23, TO_pct01_23) %>%
  select(., -3)

pct01_07$buoy <- ("07")
pct01_08$buoy <- ("08")
pct01_10$buoy <- ("10")
pct01_12$buoy <- ("12")
pct01_13$buoy <- ("13")
pct01_14$buoy <- ("14")
pct01_16$buoy <- ("16")
pct01_18$buoy <- ("18")
pct01_19$buoy <- ("19")
pct01_20$buoy <- ("20")
pct01_21$buoy <- ("21")
pct01_22$buoy <- ("22")
pct01_23$buoy <- ("23")

pct01_all <- rbind(pct01_07, pct01_08, pct01_10, pct01_12, pct01_13,
                   pct01_14, pct01_16, pct01_18, pct01_19, pct01_20,
                   pct01_21, pct01_22, pct01_23)

# Group by and summarize
pct01_all %>%
  group_by(buoy) %>%
  summarize(max(`TOL_125`))

Create df from 99 percentile
```{r}
# 99 Percentile
pct99_07 <- cbind(BB_pct99_07, TO_pct99_07) %>%
  select(., -3)
pct99_08 <- cbind(BB_pct99_08, TO_pct99_08) %>%
  select(., -3)
pct99_10 <- cbind(BB_pct99_10, TO_pct99_10) %>%
  select(., -3)
pct99_12 <- cbind(BB_pct99_12, TO_pct99_12) %>%
  select(., -3)
pct99_13 <- cbind(BB_pct99_13, TO_pct99_13) %>%
  select(., -3)
pct99_14 <- cbind(BB_pct99_14, TO_pct99_14) %>%
  select(., -3)
pct99_16 <- cbind(BB_pct99_16, TO_pct99_16) %>%
  select(., -3)
pct99_18 <- cbind(BB_pct99_18, TO_pct99_18) %>%
  select(., -3)
pct99_19 <- cbind(BB_pct99_19, TO_pct99_19) %>%
  select(., -3)
pct99_20 <- cbind(BB_pct99_20, TO_pct99_20) %>%
  select(., -3)
pct99_21 <- cbind(BB_pct99_21, TO_pct99_21) %>%
  select(., -3)
pct99_22 <- cbind(BB_pct99_22, TO_pct99_22) %>%
  select(., -3)
pct99_23 <- cbind(BB_pct99_23, TO_pct99_23) %>%
  select(., -3)

# Add column with buoy number
pct99_07$buoy <- ("07")
pct99_08$buoy <- ("08")
pct99_10$buoy <- ("10")
pct99_12$buoy <- ("12")
pct99_13$buoy <- ("13")
pct99_14$buoy <- ("14")
pct99_16$buoy <- ("16")
pct99_18$buoy <- ("18")
pct99_19$buoy <- ("19")
pct99_20$buoy <- ("20")
pct99_21$buoy <- ("21")
pct99_22$buoy <- ("22")
pct99_23$buoy <- ("23")

pct99_all <- rbind(pct99_07, pct99_08, pct99_10, pct99_12, pct99_13,
                   pct99_14, pct99_16, pct99_18, pct99_19, pct99_20,
                   pct99_21, pct99_22, pct99_23)
```

Plot 99pct and 1pct by buoy
```{r fig.height=5, fig.width=13}
# Group by and summarize
pct99_all %>%
  group_by(buoy) %>%
  summarize(max(`TOL_125`)) %>%
  ggplot(aes(x = buoy, y = `max(TOL_125)`)) + geom_bar(stat = "identity")

#TOL timeline by buoy
pct99_all %>%
  ggplot(aes(x = dateTime, y = TOL_2000, color = buoy)) + geom_line()

# Average dB by hour for each frequency
pct99_16 %>%
  group_by(time = floor_date(dateTime, "1 hour")) %>%
  summarize(mean_BB = mean(`BB_20-24000`),
            meanTOL_125 = mean(TOL_125),
            meanTOL_250 = mean(TOL_250),
            meanTOL_500 = mean(TOL_500),
            meanTOL_2000 = mean(TOL_2000),
            meanTOL_4000 = mean(TOL_4000),
            meanTOL_20000 = mean(TOL_20000)) %>%
  pivot_longer(cols = mean_BB:meanTOL_20000,
               names_to = "frequency",
               values_to="dB") %>%
  ggplot(aes(x = time, y = dB)) + geom_line(aes(color = frequency)) #+
  #geom_point(data = allDrifts, aes(color = species))
# Show more dates/times on x axis
# 99pct, buoy 16 has a strong peak later in journey at 4kHz

ggplot() +
  geom_point(data = pct01_23, aes(x = lubridate::round_date(dateTime, "2 hours"), y = TOL_125), color = 'steelblue') +
  #geom_line(data = pct99_23, aes(x = dateTime, y = TOL_125), color = 'coral') +
  facet_grid()

Bind percentile df (pctx_x) with GPS track df (GPSwhalex)

Buoy 7
```{r}
# Create columns with percentiles and BIND
pct50_07_select <- pct50_07 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_07_select <- pct10_07 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_07_select <- pct90_07 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct07 <- cbind(pct10_07_select, pct50_07_select, pct90_07_select)

# Join GPS points with the three percentiles
pct07_whl <- timeJoin(GPSwhale7, pct07, thresh = 3600, interpolate = FALSE)

#Summarize
buoy7pctSummary <- pct07_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 8
```{r}
# Create columns with percentiles and BIND
pct50_08_select <- pct50_08 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_08_select <- pct10_08 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_08_select <- pct90_08 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct08 <- cbind(pct10_08_select, pct50_08_select, pct90_08_select)

# Join GPS points with the three percentiles
pct08_whl <- timeJoin(GPSwhale8, pct08, thresh = 3600, interpolate = FALSE)

#Summarize
buoy8pctSummary <- pct08_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 10
```{r}
# Create columns with percentiles and BIND
pct50_10_select <- pct50_10 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_10_select <- pct10_10 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_10_select <- pct90_10 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct10 <- cbind(pct10_10_select, pct50_10_select, pct90_10_select)

# Join GPS points with the three percentiles
pct10_whl <- timeJoin(GPSwhale10, pct10, thresh = 3600, interpolate = FALSE)

#Summarize
buoy10pctSummary <- pct10_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 12
```{r}
# Create columns with percentiles and BIND
pct50_12_select <- pct50_12 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_12_select <- pct10_12 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_12_select <- pct90_12 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct12 <- cbind(pct10_12_select, pct50_12_select, pct90_12_select)

# Join GPS points with the three percentiles
pct12_whl <- timeJoin(GPSwhale12, pct12, thresh = 3600, interpolate = FALSE)

#Summarize
buoy12pctSummary <- pct12_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 13
```{r}
# Create columns with percentiles and BIND
pct50_13_select <- pct50_13 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_13_select <- pct10_13 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_13_select <- pct90_13 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct13 <- cbind(pct10_13_select, pct50_13_select, pct90_13_select)

# Join GPS points with the three percentiles
pct13_whl <- timeJoin(GPSwhale13, pct13, thresh = 3600, interpolate = FALSE)

#Summarize
buoy13pctSummary <- pct13_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 14 # Issue binding pct50 with others due to differing number of rows
```{r}
# Create columns with percentiles and BIND
pct50_14_select <- pct50_14 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_14_select <- pct10_14 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_14_select <- pct90_14 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
#pct14 <- cbind(pct10_14_select, pct50_14_select, pct90_14_select)

# Join GPS points with the three percentiles
pct14_whl <- timeJoin(GPSwhale14, pct14, thresh = 3600, interpolate = FALSE)

#Summarize
buoy14pctSummary <- pct14_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```
Buoy 16
```{r}
# Create columns with percentiles and BIND
pct50_16_select <- pct50_16 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_16_select <- pct10_16 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_16_select <- pct90_16 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct16 <- cbind(pct10_16_select, pct50_16_select, pct90_16_select)

# Join GPS points with the three percentiles
pct16_whl <- timeJoin(GPSwhale16, pct16, thresh = 3600, interpolate = FALSE)

#Summarize
buoy16pctSummary <- pct16_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 18
```{r}
# Create columns with percentiles and BIND
pct50_18_select <- pct50_18 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_18_select <- pct10_18 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_18_select <- pct90_18 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct18 <- cbind(pct10_18_select, pct50_18_select, pct90_18_select)

# Join GPS points with the three percentiles
pct18_whl <- timeJoin(GPSwhale18, pct18, thresh = 3600, interpolate = FALSE)

#Summarize
buoy18pctSummary <- pct18_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 19
```{r}
# Create columns with percentiles and BIND
pct50_19_select <- pct50_19 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_19_select <- pct10_19 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_19_select <- pct90_19 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct19 <- cbind(pct10_19_select, pct50_19_select, pct90_19_select)

# Join GPS points with the three percentiles
pct19_whl <- timeJoin(GPSwhale19, pct19, thresh = 3600, interpolate = FALSE)

#Summarize
buoy19pctSummary <- pct19_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 20
```{r}
# Create columns with percentiles and BIND
pct50_20_select <- pct50_20 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_20_select <- pct10_20 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_20_select <- pct90_20 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct20 <- cbind(pct10_20_select, pct50_20_select, pct90_20_select)

# Join GPS points with the three percentiles
pct20_whl <- timeJoin(GPSwhale20, pct20, thresh = 3600, interpolate = FALSE)

#Summarize
buoy20pctSummary <- pct20_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 21
```{r}
# Create columns with percentiles and BIND
pct50_21_select <- pct50_21 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_21_select <- pct10_21 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_21_select <- pct90_21 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct21 <- cbind(pct10_21_select, pct50_21_select, pct90_21_select)

# Join GPS points with the three percentiles
pct21_whl <- timeJoin(GPSwhale21, pct21, thresh = 3600, interpolate = FALSE)

#Summarize
buoy21pctSummary <- pct21_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 22
```{r}
# Create columns with percentiles and BIND
pct50_22_select <- pct50_22 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_22_select <- pct10_22 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_22_select <- pct90_22 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct22 <- cbind(pct10_22_select, pct50_22_select, pct90_22_select)

# Join GPS points with the three percentiles
pct22_whl <- timeJoin(GPSwhale22, pct22, thresh = 3600, interpolate = FALSE)

#Summarize
buoy22pctSummary <- pct22_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Buoy 23
```{r}
# Create columns with percentiles and BIND
pct50_23_select <- pct50_23 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_23_select <- pct10_23 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_23_select <- pct90_23 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
pct23 <- cbind(pct10_23_select, pct50_23_select, pct90_23_select)

# Join GPS points with the three percentiles
pct23_whl <- timeJoin(GPSwhale23, pct23, thresh = 3600, interpolate = FALSE)

#Summarize
buoy23pctSummary <- pct23_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

Knit all summary percentiles into a table
```{r}

## Buoy 7 ##
sumPct7 <- kable(buoy7pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 7") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 8 ##
sumPct8 <- kable(buoy8pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 8") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 10 ##
sumPct10 <- kable(buoy10pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 10") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 12 ##
sumPct12 <- kable(buoy12pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 12") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 13 ##
sumPct13 <- kable(buoy13pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 13") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 14 ##
#kable(buoy14pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
#                                     caption = "Summary Percentiles for Buoy 14") %>%
#  kableExtra::kable_classic() %>%
#  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 16 ##
sumPct16 <- kable(buoy16pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 16") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 18 ##
sumPct18 <- kable(buoy18pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 18") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 19 ##
sumPct19 <- kable(buoy19pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 19") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 20 ##
sumPct20 <- kable(buoy20pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 20") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 21 ##
sumPct21 <- kable(buoy21pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 21") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 22 ##
sumPct22 <- kable(buoy22pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 22") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

## Buoy 23 ##
sumPct23 <- kable(buoy23pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 23") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

Time Series Heat Map
```{r fig.width=12}

pdf(paste("timeSeries8-31",".pdf"), width=14, height=10)

### Buoy 7 ####
W.07 <- fulltrack07 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

W.07plot <- plotPresGrid(W.07, bin = 'hour', type = 'presence')

g1 <- (plotTimeseries(fulltrack07, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 7: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.07, bin = 'hour', type = 'presence', start = min(fulltrack07$UTC),
                         end = max(fulltrack07$UTC), fill = NA, color = "white")

# Create plot with TOL125
combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)

t1 <- plotTimeseries(fulltrack07, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 7: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.07, bin = 'hour', type = 'presence', start = min(fulltrack07$UTC),
                         end = max(fulltrack07$UTC), fill = NA, color = "white")

# Create plot with TOL2000
combined.t <- t1
combined.t$layers <- c(combined.t$layers, t2$layers)

combined.g + combined.t
```

```{r fig.width=12}
###### Buoy 8 ####
W.08 <- fulltrack08 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

W.08plot <- plotPresGrid(W.08, bin = 'hour', type = 'presence')

g1 <- (plotTimeseries(fulltrack08, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(fulltrack08$UTC),
                         end = max(fulltrack08$UTC), fill = NA, color = "white")
